---
title: "Germany Global Health Analysis"
format:
  html: 
    default: true  # Ensure HTML rendering works
    self-contained: false
    math: false
  pdf:
    pdf-engine: xelatex  # Change to xelatex to support Unicode
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load core tidyverse + plotting
pacman::p_load(tidyverse, lubridate, ggplot2, ggrepel, stringr, tibble, dplyr, janitor)

# Then load table + file manipulation
pacman::p_load(here, readxl, jsonlite, httr, knitr, data.table, tidyr, stringi, cli)

# Then load extras separately
pacman::p_load(gt, gtExtras, countrycode, stringdist, tinytex, htmltools, patchwork)
```

```{r overview, include=FALSE}
# read the df
openalex_pubmed_papers <- fread(here("data/4-results/openalex_pubmed_papers_merged_2025-05-22.csv"))
nrow(openalex_pubmed_papers)#119347

# make journal titles consistent
openalex_pubmed_papers <- openalex_pubmed_papers %>%
  mutate(journal_title = journal_title %>% str_replace("^The Lancet\\.", "The Lancet") %>%
         str_squish() %>%
         str_to_title())

openalex_pubmed_papers <- openalex_pubmed_papers %>%
  mutate(
    pmid = as.character(pmid),
    oa_id = as.character(oa_id),
    primary_id = coalesce(pmid, oa_id)
  )

papers_2024 <- openalex_pubmed_papers %>%
  filter(publication_year == "2024")
nrow(papers_2024)#20422
```

```{r affil overview, include=FALSE}
openalex_pubmed_affil <- fread(here("data/4-results/openalex_pubmed_authors_merged_2025-05-22.csv"))

# Update institution names in openalex_pubmed_affil
openalex_pubmed_affil <- openalex_pubmed_affil %>%
  mutate(institution_display_name = case_when(
    institution_display_name == "German Center for Infection Research" ~ "German Center for Infection Research (DZIF)",
    institution_display_name == "Federal Institute for Risk Assessment" ~ "Federal Institute for Risk Assessment (BfR)",
    TRUE ~ institution_display_name  # This line ensures all other values stay untouched
  ))

# Check if the 'institution_country_code' column exists
if ("institution_country_code" %in% names(openalex_pubmed_affil)) {
  # Transform the 2-letter country codes to country names
  openalex_pubmed_affil[, country_name := countrycode(institution_country_code,
                                                     origin = "iso2c",
                                                     destination = "country.name")]

  # Set "XK" to "Kosovo" in the country_name column
  openalex_pubmed_affil[institution_country_code == "XK", country_name := "Kosovo"]

  # You can now work with the 'country_name' column in your data.table
  print(head(openalex_pubmed_affil[, .(institution_country_code, country_name)]))
} else {
  cat("Error: The 'institution_country_code' column was not found in the data.table.\n")
}

openalex_pubmed_affil <- openalex_pubmed_affil %>%
  mutate(primary_id = coalesce(as.character(pmid), as.character(oa_id)))

length(unique(openalex_pubmed_affil$primary_id))#115864

affil_2024 <- openalex_pubmed_affil %>%
  filter(primary_id %in% papers_2024$primary_id)
length(unique(affil_2024$primary_id))#19049

na_institution_name <- openalex_pubmed_affil %>% filter(is.na(institution_display_name)) %>% nrow()
na_country <- openalex_pubmed_affil %>% filter(is.na(institution_country_code)) %>% nrow()
na_institution_name_perc <- na_institution_name / nrow(openalex_pubmed_affil)
na_country_perc <- na_country / nrow(openalex_pubmed_affil)
```

### Overview

The datasets we are analyzing are from two means:

- **Papers with “global health”** in title or abstract on OpenAlex / PubMed  
- **All papers** in the following journals:

  - *The Lancet Global Health*  
  - *Bulletin of the World Health Organization*  
  - *The Lancet Planetary Health*  
  - *BMJ Global Health*  
  - *Globalization and Health*  
  - *Pathogens and Global Health*  
  - *Journal of Global Health*  
  - *Global Health Research and Policy*  
  - *Journal of Epidemiology and Global Health*  
  - *Cambridge Prisms: Global Mental Health*  
  - *Annals of Global Health*  
  - *Global Health: Science and Practice*  
  - *Global Public Health*  
  - *Clinical Epidemiology and Global Health*  
  - *Global Health Action*  
  - *Global Health Promotion*  
  - *PLOS Global Public Health*
 
Note: We only look at non-retracted, published articles of the following type: article, review, book, book-chapter, editorial, letter, report, case reports, meta analysis, comment, systematic review, comparative study.

```{r ggplot source, include=FALSE}
# whether the paper is from openalex or pubmed
n_openalex <- openalex_pubmed_papers %>% filter(from_openalex == TRUE) %>% nrow()
n_pubmed <- openalex_pubmed_papers %>% filter(from_pubmed == TRUE) %>% nrow()
n_both <- openalex_pubmed_papers %>%
  filter(from_openalex == TRUE & from_pubmed == TRUE) %>%
  nrow()

plot_paper_source <- tibble(
  Source = c("OpenAlex Only", "PubMed Only", "Both"),
  Count = c(
    n_openalex - n_both,
    n_pubmed - n_both,
    n_both
  )
)

# whether the author affil is from openalex or pubmed
id_source_summary <- openalex_pubmed_affil %>%
  distinct(primary_id, .keep_all = TRUE) %>%    # one row per PMID × source
  count(source, name = "Count")     # tally how many PMIDs in each source

plot_author_source <- id_source_summary %>%
  mutate(
    Source = case_when(
      source == "OpenAlex"          ~ "OpenAlex Only",
      source == "PubMed"            ~ "PubMed Only",
      source == "PubMed & OpenAlex" ~ "Both",
      TRUE                           ~ source
    )
  ) %>%
  # now select exactly the two columns we want
  select(Source, Count)

# whether the paper is from query or journal
n_query <- openalex_pubmed_papers %>% filter(origin == "query") %>% nrow()
n_journal <- openalex_pubmed_papers %>% filter(origin == "journal") %>% nrow()
n_both_origin <- openalex_pubmed_papers %>% filter(origin == "query & journal") %>% nrow()

plot_paper_origin <- tibble(
  Source = c("Query Only", "Journal Only", "Both"),
  Count = c(
    n_query,
    n_journal,
    n_both_origin
  )
)

id_origin_summary <- openalex_pubmed_affil %>%
  distinct(primary_id, .keep_all = TRUE) %>%    # one row per PMID × source
  count(origin, name = "Count")     # tally how many PMIDs in each source

plot_author_origin <- id_origin_summary %>%
  mutate(
    Source = case_when(
      origin == "query"              ~ "Query Only",
      origin == "journal"            ~ "Journal Only",
      origin == "query & journal"    ~ "Both",
      TRUE                           ~ origin
    )
  ) %>%
  # now select exactly the two columns we want
  select(Source, Count)
```

```{r plot, echo=FALSE}
shared_y_max <- max(
  plot_paper_source$Count,
  plot_author_source$Count,
  plot_paper_origin$Count,
  plot_author_origin$Count,
  na.rm = TRUE
)

plot_paper <- ggplot(plot_paper_source, aes(x = Source, y = Count, fill = Source)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::comma(Count)), vjust = -0.5, size = 4) +
  scale_fill_viridis_d(option = "D") +
  scale_y_continuous(labels = scales::comma, limits = c(0, shared_y_max * 1.25)) +
  labs(
    title    = "Paper Source Distribution",
    subtitle = glue::glue("n = {scales::comma(n_openalex - n_both + n_pubmed - n_both + n_both)}"),
    x = NULL, y = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position   = "none",
    plot.title        = element_text(hjust = 0.5),
    plot.subtitle     = element_text(hjust = 0.5)
  )

plot_author <- ggplot(plot_author_source, aes(x = Source, y = Count, fill = Source)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::comma(Count)), vjust = -0.5, size = 4) +
  scale_fill_viridis_d(option = "D") +
  scale_y_continuous(labels = scales::comma, limits = c(0, shared_y_max * 1.25)) +
  labs(
    title    = "Author Source Distribution",
    subtitle = glue::glue("n = {scales::comma(sum(plot_author_source$Count))}"),
    x = NULL, y = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position   = "none",
    plot.title        = element_text(hjust = 0.5),
    plot.subtitle     = element_text(hjust = 0.5)
  )

plot_queryjournal <- ggplot(plot_paper_origin, aes(x = Source, y = Count, fill = Source)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::comma(Count)), vjust = -0.5, size = 4) +
  scale_fill_viridis_d(option = "D") +
  scale_y_continuous(labels = scales::comma, limits = c(0, shared_y_max * 1.25)) +
  labs(
    title    = "Paper Query/Journal Distribution",
    subtitle = glue::glue("n = {scales::comma(sum(plot_paper_origin$Count))}"),
    x = NULL, y = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position   = "none",
    plot.title        = element_text(hjust = 0.5),
    plot.subtitle     = element_text(hjust = 0.5)
  )

plot_authororigin <- ggplot(plot_author_origin, aes(x = Source, y = Count, fill = Source)) +
  geom_col(width = 0.6) +
  geom_text(aes(label = scales::comma(Count)), vjust = -0.5, size = 4) +
  scale_fill_viridis_d(option = "D") +
  scale_y_continuous(labels = scales::comma, limits = c(0, shared_y_max * 1.25)) +
  labs(
    title    = "Author Query/Journal Distribution",
    subtitle = glue::glue("n = {scales::comma(sum(plot_author_origin$Count))}"),
    x = NULL, y = NULL
  ) +
  theme_minimal() +
  theme(
    legend.position   = "none",
    plot.title        = element_text(hjust = 0.5),
    plot.subtitle     = element_text(hjust = 0.5)
  )

# Build a 2×2 grid, with the bottom-right cell a spacer
layout <- (plot_paper | plot_author) /
          (plot_queryjournal | plot_authororigin)

layout + plot_layout(widths = c(1,1), heights = c(1,1))
```

Out of the total records in the affiliations dataset,  `r round(na_institution_name_perc * 100, 2)`% do not have institution names recorded, and `r round(na_country_perc * 100, 2)`% are missing country information.

### Data transformation and pre-processing

1. **Source-specific deduplication**

  - **PubMed-only**: Of the original 66264 PubMed rows, we built a joint key `coalesce(doi, pmid)`, kept all rows where that key was `NA`, and for the rest collapsed any "query" vs "journal" duplicates by relabeling to "query & journal". This removed 2543 duplicate rows.
  
  - **OpenAlex-only**: Starting from 105716 OpenAlex rows, we built `coalesce(doi, pmid, oa_id)` again preserving all `NA`-key rows and collapsing query/journal duplicates in the same way. This removed 5177 duplicate rows.
  
2. **Cross-source merge**

Next we performed a full join of PubMed and OpenAlex data based on the combined key (`doi`, `pmid`). 41 600 papers appeared in both sources. After joining we coalesced every field to prefer OpenAlex's value first, falling back to PubMed only when OpenAlex was `NA.` 

3. **Affiliation matching & deduplication**

We pass all PubMed affiliation strings through the ROR API, matching 74.2% of them (67% at score = 1, 7% at 0.9-0.99), which constitutes for `r round(na_institution_name_perc * 100, 2)` of the papers. We then full-joined the ROR-parsed PubMed affiliations with OpenAlex's based on both `pmid` and `au_display_name` (author name). For affiliations that exist in both sources, we prioritized OpenAlex's values. 


### Score Distribution

```{r score distribution, echo=FALSE}
ror_affiliations_full_results <- read_excel(here("data/3-merged/ror_affiliations_full_results.xlsx"))

# Prepare count data per score
score_counts <- ror_affiliations_full_results %>%
  filter(is.finite(score)) %>%
  count(score) %>%
  arrange(score)

ggplot(score_counts, aes(x = factor(score), y = n)) +
  geom_col(fill = "#4575b4", color = "black") +
  geom_text(aes(label = n), vjust = -0.3, size = 3) +
  labs(
    title = "Distribution of ROR Confidence Scores",
    x = "Score",
    y = "Number of Affiliations"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black")
  )

```


### Score Distribution of German Institutions

```{r score distribution germany, echo=FALSE}
german_affils_with_score <- openalex_pubmed_affil %>%
  filter(str_detect(country_name, regex("Germany", ignore_case = TRUE)))

score_counts_germany <- german_affils_with_score %>%
  filter(is.finite(score)) %>%
  count(score) %>%
  arrange(score)

ggplot(score_counts_germany, aes(x = factor(score), y = n)) +
  geom_col(fill = "#4575b4", color = "black") +
  geom_text(aes(label = n), vjust = -0.3, size = 3) +
  labs(
    title = "Distribution of ROR Confidence Scores\nfor Affiliations in Germany",
    x = "Score",
    y = "Number of Affiliations"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black")
  )
```

## Top Producing Countries from 2014 to 2024

This table highlights the countries that contributed the most to global health publications between 2014 and 2024. For each paper, we extracted the list of contributing countries based on author affiliations. To avoid double-counting, we ensured each country was only counted once per paper, even if it had multiple affiliated institutions. We then aggregated the number of unique papers associated with each country and ranked them based on publication volume.

```{r countries, echo=FALSE}
# filter logic to avoid double counting different institutions in the same country
top_country <- openalex_pubmed_affil %>%
  filter(!is.na(country_name)) %>%
  distinct(primary_id, country_name, .keep_all = TRUE) %>%
  count(country_name, sort = TRUE)

top_country %>% 
  gt() %>% 
  tab_header(
    title = md("Top Producing Countries from 2014 to 2024")
  ) %>%
  cols_label(
    country_name = "Country",
    n = "Number of Papers"
  ) %>%
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```

## Top Producing Countries in 2024

This table shows the countries that contributed the most to global health publications in the year 2024, based on unique paper counts by country.

```{r top country 2024, echo=FALSE}
top_country_2024 <- affil_2024 %>%
  filter(!is.na(country_name)) %>%
  distinct(primary_id, country_name, .keep_all = TRUE) %>%
  count(country_name, sort = TRUE)

top_country_2024 %>% 
  gt() %>% 
  tab_header(
    title = md("Top Producing Countries in 2024")
  ) %>%
  cols_label(
    country_name = "Country",
    n = "Number of Papers"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```
## Number of publications by country by year

This table shows the top 10 countries in terms of the number of global health publications per year from 2014 to 2024. Each row represents a country, with yearly publication counts, the Compound Annual Growth Rate (CAGR) over the 11-year period, and a trendline visualization. In the trendline, purple dot represents the **first value** in the trend (i.e., the value in 2014) and green dot represents the **last value** in the trend (i.e., the value in 2024). 

Leading example: Switzerland had 149 publications in 2014, increasing to 518 in 2024, with a CAGR of 13.27%, meaning the number of publications grew by 13.27% per year on average, compounded annually. The Switzerland trendline shows strong early growth in publications, peaking around 2023, followed by a slight decline. The green dot (2024 data) sits lower than the peak and appears to the left, signaling that while there's been growth overall, 2024 saw a tapering off rather than continued upward movement.

```{r publications by country by year, echo=FALSE}
paper_years <- openalex_pubmed_papers %>%
  mutate(
    publication_year = as.character(publication_year)
  ) %>%
  select(primary_id, publication_year) %>%
  filter(publication_year != "2025")

affil_country <- openalex_pubmed_affil %>%
  filter(!is.na(country_name)) %>%
  select(primary_id, country_name) %>%
  distinct()  # Remove duplicates

country_year_data <- suppressWarnings(
  left_join(affil_country, paper_years, by = "primary_id")
) %>%
  filter(!is.na(publication_year))

country_year_counts <- country_year_data %>%
  distinct(primary_id, country_name, publication_year) %>%
  count(country_name, publication_year)

top_10_countries <- country_year_counts %>%
  group_by(country_name) %>%
  summarise(total = sum(n), .groups = "drop") %>%
  arrange(desc(total)) %>%
  slice_head(n = 10) %>%
  pull(country_name)

top_country_years <- country_year_counts %>%
  filter(country_name %in% top_10_countries) %>%
  pivot_wider(names_from = publication_year, values_from = n, values_fill = 0) %>%
  arrange(desc(rowSums(across(where(is.numeric)))))

top_country_years <- top_country_years %>%
  rowwise() %>%
  mutate(
    aggr = {
      vals <- c_across(`2014`:`2024`)
      if (length(vals) > 1 && vals[1] > 0) {
        round(((vals[length(vals)] / vals[1])^(1 / (length(vals) - 1)) - 1) * 100, 2)
      } else {
        NA_real_
      }
    },
    trend = list(c_across(`2014`:`2024`))
  ) %>%
  ungroup()

top_country_years %>%
  gt() %>%
  gt_plt_sparkline(trend, type = "default") %>%
  tab_header(title = "Top 10 Countries by Yearly Publications (2014–2024)") %>%
  cols_label(
    country_name = "Country",
    trend = "Trendline",
    aggr = "Compound Annual Growth Rate (%)"
  ) %>%
  fmt_number(
    columns = aggr,
    decimals = 2
  ) %>%
  tab_options(
    table.font.size = px(13),
    heading.align = "center"
  )
```

## Top German institutions producing global health research from 2014 to 2024

The table highlights the German institutions that contributed the most to global health publications between 2014 and 2024. For each paper, we extracted the list of contributing institutions from author affiliations. To avoid double-counting, we ensured each institution was only counted once per paper, even it had multiple authors from the same institution. We then aggregated the number of unique papers associated with each institution and ranked them based on publication volume.

```{r institute DE, echo=FALSE}
# Ensure the identifier is unique for each institution
top_institutions_germany <- openalex_pubmed_affil %>%
  filter(!is.na(institution_display_name)) %>%
  filter(country_name == "Germany") %>%
  distinct(primary_id, institution_display_name, .keep_all = TRUE) %>%
  count(institution_display_name, sort = TRUE)

top_institutions_germany %>% 
  gt() %>% 
  tab_header(
    title = md("Top German Institutions from 2014 to 2024")
  ) %>%
  cols_label(
    institution_display_name = "Institution Name",
    n = "Number of Papers"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```

## Top German Institutions in 2024

This table shows the contributing German institutions to global health publications in the year 2024.

```{r institute DE 2024, echo=FALSE}
top_institutions_germany_2024 <- affil_2024 %>%
  filter(!is.na(institution_display_name)) %>%
  filter(country_name == "Germany") %>%
  distinct(primary_id, institution_display_name, .keep_all = TRUE) %>%
  count(institution_display_name, sort = TRUE)

top_institutions_germany_2024 %>% 
  gt() %>% 
  tab_header(
    title = md("Top Germany Institutions in 2024")
  ) %>%
  cols_label(
    institution_display_name = "Institution Name",
    n = "Number of Papers"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```

## All articles with German affiliation

This table shows the basic information of articles that have at least one affiliation in Germany.

```{r german articles, echo=FALSE}
# Step 1: Create primary paper info with citation and ID
all_papers_count <- openalex_pubmed_papers %>%
  mutate(
    num_citations = coalesce(num_citations_cf, num_citations, 0),
  ) %>%
  select(primary_id, title, abstract, journal_title, publication_date, url, publication_year, num_citations)

# Step 2: Prepare author names, fallback to first_name + last_name
check_papers_author <- openalex_pubmed_affil %>%
  filter(!is.na(primary_id) & !is.na(au_display_name)) %>%
  group_by(primary_id) %>%
  summarise(
    author_list = paste(unique(au_display_name), collapse = "; "),
    .groups = "drop"
  )

# Step 3: Identify papers with at least one German affiliation
german_primary_ids <- openalex_pubmed_affil %>%
  filter(country_name == "Germany" & !is.na(primary_id)) %>%
  distinct(primary_id) %>%
  pull(primary_id)

# Step 4: Merge metadata and filter German papers
germany_papers <- all_papers_count %>%
  filter(primary_id %in% german_primary_ids) %>%
  left_join(check_papers_author, by = "primary_id") %>%
  relocate(publication_year, .after = publication_date)

germany_papers$abstract <- str_remove_all(germany_papers$abstract, "<h3>.*?</h3>")
germany_papers$abstract <- str_trim(germany_papers$abstract)

# Step 5: Add abstract column with Read More/Less toggle
sanitize_text <- function(text) {
  text %>%
    str_replace_all("&", "and") %>%
    str_replace_all("['’“”—]", "") %>%
    str_replace_all("–", "-") %>%
    stringi::stri_trans_general("Latin-ASCII")
}

sanitize_text_safe <- function(text) {
  ifelse(is.na(text), NA, sanitize_text(text))
}

# Sanitize before adding read-more
germany_papers <- germany_papers %>%
  mutate(across(c(title, abstract, author_list), sanitize_text_safe)) 

germany_papers <- germany_papers %>%
  filter(publication_year != "2025")
```

```{r big table, echo=FALSE, warning=FALSE}
# Then build read-more content
germany_papers_prepped <- germany_papers %>%
  mutate(
    url = ifelse(
      !is.na(url),
      paste0('<a href="', url, '" target="_blank">Link</a>'),
      NA_character_
    ),
    abstract = ifelse(
      !is.na(abstract) & nchar(abstract) > 100,
      paste0(
        substr(abstract, 1, 100),
        '... <a href="javascript:void(0)" class="read-more">Read more</a>',
        '<span class="full-abstract" style="display:none;">',
        substr(abstract, 101, nchar(abstract)),
        '</span> <a href="javascript:void(0)" class="read-less" style="display:none;"> Read less</a>'
      ),
      abstract
    ),
    author_list = ifelse(
      !is.na(author_list) & nchar(author_list) > 100,
      paste0(
        substr(author_list, 1, 100),
        '... <a href="javascript:void(0)" class="read-more">Read more</a>',
        '<span class="full-abstract" style="display:none;">',
        substr(author_list, 101, nchar(author_list)),
        '</span> <a href="javascript:void(0)" class="read-less" style="display:none;"> Read less</a>'
      ),
      author_list
    )
  )


# Step 6: Display in interactive GT table
# Use the cleaned, prepped data for rendering
germany_papers_prepped %>%
  select(title, abstract, journal_title, publication_date, publication_year, url, author_list, num_citations) %>%
  gt() %>%
  fmt_markdown(columns = c("url", "abstract", "author_list")) %>%
  cols_label(
    title = "Paper Title",
    abstract = "Abstract",
    journal_title = "Journal Title",
    publication_date = "Publication Date",
    publication_year = "Publication Year",
    url = "Link",
    author_list = "Authors",
    num_citations = "Citation Counts"
  ) %>%
  sub_missing(columns = everything(), missing_text = "-") %>%
  opt_interactive(
    use_search = TRUE,
    use_sorting = TRUE,
    use_filters = TRUE,
    page_size_default = 20
  ) %>%
  tab_options(
    table.font.size = px(14),
    table.border.top.width = px(0),
    heading.align = "center"
  ) 
```

<script>
  document.addEventListener('DOMContentLoaded', function() {
    document.querySelectorAll('.read-more').forEach(function(link) {
      link.addEventListener('click', function(e) {
        e.preventDefault();
        const full = this.nextElementSibling;
        const less = full.nextElementSibling;
        full.style.display = 'inline';
        less.style.display = 'inline';
        this.style.display = 'none';
      });
    });

    document.querySelectorAll('.read-less').forEach(function(link) {
      link.addEventListener('click', function(e) {
        e.preventDefault();
        const full = this.previousElementSibling;
        const more = full.previousElementSibling;
        full.style.display = 'none';
        this.style.display = 'none';
        more.style.display = 'inline';
      });
    });
  });
</script>


## Top Journals for Global Health Publications

```{r global journal, echo=FALSE}
check_papers <- openalex_pubmed_affil %>%
  group_by(primary_id) %>%
  summarise(
    all_countries = paste(unique(country_name[!is.na(country_name)]), collapse = "; "),  # Concatenate unique countries
    .groups = "drop"
  )

all_journal <- all_papers_count %>%
  left_join(check_papers, by = "primary_id") %>%  # Merge country info
  filter(!is.na(all_countries)) # Ensure only papers with country data remain

top_journals <- all_journal %>%
  filter(!is.na(journal_title)) %>%
  count(journal_title, sort = TRUE)

top_journals %>%
  gt() %>%
  tab_header(
    title = "Top Journals of Global Institutions"
  ) %>%
  cols_label(
    journal_title = "Journal",
    n = "Number of Publications"
  ) %>%
  opt_interactive(
    use_search = FALSE,
    use_sorting = TRUE,
    use_filters = TRUE,
    page_size_default = 10
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.align = "center"
  )
```


## Top Journals for Germany Global Health Publications

Of all articles that had an author with at least one affiliation in Germany, 155 articles were published in PLOS ONE.

```{r german journals, echo=FALSE}
germany_journal <- all_papers_count %>%
  left_join(check_papers, by = "primary_id") %>%  # Merge country info
  filter(!is.na(all_countries)) %>%  # Ensure only papers with country data remain
  filter(str_detect(all_countries, "Germany"))

# Create table of top journals based on number of publications
top_german_journals <- germany_journal %>%
  filter(!is.na(journal_title)) %>%
  count(journal_title, sort = TRUE) %>%
  slice_head(n = 10)  # Adjust this number if needed

top_german_journals %>%
  gt() %>%
  tab_header(
    title = "Top Journals of German Institutions"
  ) %>%
  cols_label(
    journal_title = "Journal",
    n = "Number of Publications"
  ) %>%
  opt_interactive(
    use_search = FALSE,
    use_sorting = TRUE,
    use_filters = TRUE,
    page_size_default = 10
  ) %>%
  tab_options(
    table.font.size = px(14),
    heading.align = "center"
  )
```

## Frequency table of Keywords and MESH terms from top global health journals

Frequency distribution of author-assigned keywords and indexed MeSH (Medical Subject Headings) terms in articles published in The Lancet Global Health and BMJ Global Health. This visualization highlights thematic emphasis and term usage patterns across global health journals.

```{r frequency table, echo=FALSE, warning=FALSE, message=FALSE}
# 1. Generate frequency tables for all journals
journals <- c("The Lancet Global Health", "Bmj Global Health")

# Helper function to generate keyword and MeSH frequency tables
generate_freq_tables <- function(data, journal_name) {
  data_filtered <- data %>%
    filter(str_to_lower(journal_title) == str_to_lower(journal_name))
  
  # Keyword frequency table
  keyword_freq <- data_filtered %>%
    filter(!is.na(keywords)) %>%
    mutate(keyword = strsplit(keywords, ";|,")) %>%
    unnest(keyword) %>%
    mutate(keyword = str_trim(str_to_lower(keyword))) %>%
    filter(keyword != "") %>%
    count(keyword, sort = TRUE) %>%
    rename(term = keyword, frequency = n)
  
  # MeSH frequency table
  mesh_freq <- data_filtered %>%
    filter(!is.na(MESH_terms)) %>%
    mutate(mesh = strsplit(MESH_terms, ";|,")) %>%
    unnest(mesh) %>%
    mutate(mesh = str_trim(str_to_lower(mesh))) %>%
    filter(mesh != "") %>%
    count(mesh, sort = TRUE) %>%
    rename(term = mesh, frequency = n)
  
  return(list(
    keyword = keyword_freq,
    mesh = mesh_freq
  ))
}

all_freqs <- lapply(journals, function(journal) {
  tables <- generate_freq_tables(openalex_pubmed_papers, journal)
  list(
    keyword = mutate(tables$keyword, journal = journal),
    mesh = mutate(tables$mesh, journal = journal)
  )
})

# 2. Combine into two big tables
all_keywords <- bind_rows(lapply(all_freqs, function(x) x$keyword)) %>%
  relocate(journal, .before = term)

all_mesh <- bind_rows(lapply(all_freqs, function(x) x$mesh)) %>%
  relocate(journal, .before = term)

# 3. Optional: Show only top N terms per journal
top_n_per_journal <- function(df, n = 15) {
  df %>%
    group_by(journal) %>%
    slice_max(frequency, n = n, with_ties = FALSE) %>%
    ungroup()
}

keywords_top <- top_n_per_journal(all_keywords, n = 15)
mesh_top <- top_n_per_journal(all_mesh, n = 15)

# 4. Render GT tables
render_freq_table_multi <- function(df, title) {
  gt(df) %>%
    tab_header(title = title) %>%
    fmt_number(columns = frequency, decimals = 0) %>%
    cols_label(
      journal = "Journal",
      term = "Term",
      frequency = "Frequency"
    ) %>%
    tab_options(
      table.font.size = px(12),
      data_row.padding = px(2),
      table.width = pct(80),
      heading.align = "left"
    )
}

# 5. Display both tables
render_freq_table_multi(keywords_top, "Top Keywords Across Selected Journals")
render_freq_table_multi(mesh_top, "Top MeSH Terms Across Selected Journals")
```


## Top 1000 Global Institutions from 2014 to 2024

The top 1000 global institutions producing global health publications from 2014 to 2024 (limiting to 100 to avoid printing an extremely large table of 47k+ rows).

```{r institutions, echo=FALSE}
# Ensure the identifier is unique for each institution
top_institutions_global <- openalex_pubmed_affil %>%
  filter(!is.na(institution_display_name)) %>%
  distinct(primary_id, institution_display_name, country_name, .keep_all = TRUE) %>%
  count(institution_display_name, country_name, sort = TRUE)

top_institutions_global %>% 
  slice_head(n = 1000) %>%
  gt() %>% 
  tab_header(
    title = md("Top 1000 Global Institutions from 2014 to 2024")
  ) %>%
  cols_label(
    institution_display_name = "Institution Name",
    country_name = "Country",
    n = "Number of Papers"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```

Here presents 50 randomly chosen papers produced by London School of Hygiene & Tropical Medicine.

```{r inspect paper, echo=FALSE}
top_inst_paper <- openalex_pubmed_affil %>%
  filter(institution_display_name == "London School of Hygiene & Tropical Medicine") %>%
  select(primary_id)

paper_titles <- openalex_pubmed_papers %>%
  filter(primary_id %in% top_inst_paper$primary_id) %>%
  sample_n(50)

paper_titles %>% 
  select(title, journal_title, publication_date, doi) %>%
  gt() %>% 
  cols_label(
    title = "Paper Title",
    journal_title = "Journal Title",
    publication_date = "Publication Date",
    doi = "DOI"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = TRUE,  
    use_sorting = TRUE,  
    use_filters = TRUE,  
    page_size_default = 10  
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```


## Top 1000 Global Institutions in 2024

The top 1000 global institutions producing global health publications in 2024 (limiting to 100 to avoid printing an extremely large table of 41k+ rows).

```{r institutions 2024, echo=FALSE}
# Ensure the identifier is unique for each institution
top_institutions_global_24 <- affil_2024 %>%
  filter(!is.na(institution_display_name)) %>%
  distinct(primary_id, institution_display_name, country_name, .keep_all = TRUE) %>%
  count(institution_display_name, country_name, sort = TRUE)

top_institutions_global_24 %>% 
  slice_head(n = 1000) %>%
  gt() %>% 
  tab_header(
    title = md("Top 1000 Global Institutions in 2024")
  ) %>%
  cols_label(
    institution_display_name = "Institution Name",
    country_name = "Country",
    n = "Number of Papers"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```


## Co-publishing between countries (Germany's partners)

This table is constructed by identifying all global health research papers that include at least one contributor affiliated with Germany. For each of these papers, we extract all other countries that are listed as collaborators. Then, we count the frequency of each non-German country appearing in these papers. The resulting count represents the number of collaborative papers between Germany and each partner country, ranked from highest to lowest based on how often they appear as co-authors with Germany. For example, if the United States appears in 1,005 such papers, it means that Germany and the U.S. have co-published 1,005 papers together during 2014-2024.

```{r co-publishing countries, echo=FALSE}
germany_collab <- all_papers_count %>%
  left_join(check_papers, by = "primary_id") %>%  # Merge country info
  filter(!is.na(all_countries)) %>%  # Ensure only papers with country data remain
  filter(all_countries != "Germany") %>%  # Filter for papers involving Germany
  filter(str_detect(all_countries, "Germany"))

germany_collab_expanded <- germany_collab %>%
  separate_rows(all_countries, sep = "; ") %>%  # Split into multiple rows
  filter(all_countries != "Germany")  # Remove Germany itself to get co-countries

germany_network_table <- germany_collab_expanded %>%
  group_by(all_countries) %>%
  summarise(paper_count = n_distinct(primary_id), .groups = "drop") %>%
  arrange(desc(paper_count))  # Sort by most collaborations

germany_network_table %>% 
  gt() %>% 
  tab_header(
    title = md("Germany's Top Collaborating Countries in Global Health Publications")
  ) %>%
  cols_label(
    paper_count = "Number of Collaborative Papers",
    all_countries = "Countries"
  ) %>% 
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14), 
    table.border.top.width = px(0),  
    heading.align = "center"  
  )
```

## Co-publishing between institutions (Germany & global institutions)

This table is generated by first identifying all research papers in global health that include at least one German institution among the contributors. For each of these papers, we extract the names of all other institutions worldwide that also appear as co-authors. We then count how frequently each non-German institution appears in these collaborative papers. The result shows the number of times a given institution has co-published with German institutions. The table is then sorted by the number of papers, highlighting the top institutional collaborators with Germany. For instance, if the University of Oxford appears in 117 papers, it means it has collaborated in 117 papers with at least one German institution.

```{r co-publishing institutions, echo=FALSE}
# Get all paper IDs where Germany is one of the countries
check_papers_german <- check_papers %>%
  filter(str_detect(all_countries, "Germany")) %>%
  pull(primary_id)

# Get all institutions
institution_collab <- openalex_pubmed_affil %>%
  filter(primary_id %in% check_papers_german) %>%  # only papers involving Germany
  filter(!is.na(institution_display_name), country_name != "Germany")  # exclude German institutions

# Count how many German papers each institution appears in
top_collab_institutions <- institution_collab %>%
  group_by(institution_display_name, country_name) %>%
  summarise(paper_count = n_distinct(primary_id), .groups = "drop") %>%
  arrange(desc(paper_count))

top_collab_institutions %>%
  gt() %>%
  tab_header(title = "Top Institutions Collaborating with Germany in Global Health") %>%
  cols_label(
    institution_display_name = "Institution",
    country_name = "Country",
    paper_count = "Number of Collaborative Papers"
  ) %>%
  sub_missing(columns = everything(), missing_text = "-") %>% 
  opt_interactive(
    use_search = FALSE, 
    use_sorting = TRUE, 
    use_filters = TRUE,  
    page_size_default = 10 
  ) %>%
  tab_options(
    table.font.size = px(14)
  )
```

## Most Cited German Global Health Papers

Here we include all German papers ranked by citation counts, including papers that did not provide country information.

```{r citations, echo=FALSE}
all_papers_count_top_10_germany <- all_papers_count %>%
  left_join(check_papers, by = "primary_id") %>%  # Merge country info
  filter(str_detect(all_countries, "Germany")) %>%  # Filter for papers involving Germany
  arrange(desc(num_citations))  # Re-rank after filtering

# Create a table using gt
all_papers_count_top_10_germany %>%
  select(-abstract) %>%
  slice_head(n = 10) %>%
  select(-primary_id) %>%  # Remove primary_id before visualization
  gt() %>%
  tab_header(
    title = "Top 10 Most Cited German Global Health Papers"
  ) %>%
  cols_label(
    title = "Paper Title",
    num_citations = "Number of Citations",
    publication_year = "Year",
    journal_title = "Journal Title",
    all_countries = "Involved Countries"
  ) %>%
  fmt_number(
    columns = num_citations, decimals = 0  # Ensure citation counts are whole numbers
  ) %>%
  opt_interactive(  # Enables search, sorting, and filtering
    use_search = TRUE,  
    use_sorting = TRUE,  
    use_filters = TRUE,  
    page_size_default = 10  # Adjust rows per page
  ) %>%
  tab_options(
    table.font.size = px(11)  # Ensures better readability
  )
```

## Most Cited International Global Health Papers

Here we include all papers ranked by citation counts, even if some papers did not provide country information.

```{r all paper citation, echo=FALSE}
# Check the papers with the same title
all_papers <- openalex_pubmed_papers %>%
  mutate(title = str_squish(title)) %>%
  group_by(title) %>%
  filter(n()>1) %>%
  ungroup()
#nrow(all_papers) #9649 rows of duplicated papers but different versions and sometimes different abstracts
  
all_papers_count_top_10 <- all_papers_count %>%
  left_join(check_papers, by = "primary_id") %>%  # Merge country info
    # Ensure only papers with country data remain
  arrange(desc(num_citations)) %>%  # Re-rank after filtering
  slice_head(n = 10)  # Extract top 10 papers

# Create a table using gt
all_papers_count_top_10 %>%
  select(-primary_id, -abstract) %>%  # Remove primary_id before visualization
  gt() %>%
  tab_header(
    title = "Top 10 Most Cited International Global Health Papers"
  ) %>%
  cols_label(
    title = "Paper Title",
    num_citations = "Number of Citations",
    publication_year = "Year",
    journal_title = "Journal Title",
    all_countries = "Involved Countries"
  ) %>%
  fmt_number(
    columns = num_citations, decimals = 0  # Ensure citation counts are whole numbers
  ) %>%
  opt_interactive(  # Enables search, sorting, and filtering
    use_search = TRUE,  
    use_sorting = TRUE,  
    use_filters = TRUE,  
    page_size_default = 10  # Adjust rows per page
  ) %>%
  tab_options(
    table.font.size = px(11)
  )
```

